The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications

### 2017-04-04 paper.tex
added bits to paragraph on Reck et al.

\comment{Discuss the Reck et al. decomposition}

>>>>

\comment{Discuss the Reck et al. decomposition}
The task of implementing an arbitrary quantum computation on linear optics comes down to implementing an arbitrary $n\times n$ unitary matrix. If a non-unitary transformation is desired, it can be embedded within a unitary matrix with larger dimensions. An algorithm for expressing an arbitrary unitary matrix in terms of beamsplitters and phase-shifters, or equivalently Mach-Zedner interferometers, exists \cite{bib:Reck1994,bib:Englert2001} and has been widely used {\bf (find examples)}. Later, it has been shown that any nontrivial beam splitter is universal for linear optics \cite{bib:Bouland2014}.
